---
title: "Clone Code"
author: "Beth Clifton Holcomb"
date: "3/5/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
I selected Kevin Soo's National Park repo to copy because i was looking for something on an interesting topic that i wouldn't struggle to understand. his code is well documented if not a bit overly noted. it seems to be a story or assignment but for this purpose, i am able to clone and explain without too much trouble. 
there are a couple objectives the chunks are designed to show results for:

1. get visitor totals by year for all the parks
2. select the top 10 visited parks
3. graphing the increase in visitation
4. increase of visitation by percentage 
5. plotting visitation since 1916 for the top 10 visited parks
6. plotting visitation by percentage of total visitors 
7. area per visitor to each park

here is the first chunk as an example: 

This code chunk results in total visitors to each park each year data is available. it also picks the 10 parks with the highest visitiation 
```{r}
knitr::opts_chunk$set(echo = TRUE)

# load packages
library(tidyverse)
library(ggthemes)
library(cowplot)
library(ggrepel)

# load data
load("parkVisits.Rda")

# get total by year
totals <- parks %>% group_by(Year) %>%
    summarise(YearTotal = sum(Visitors))

# merge
parks <- inner_join(parks, totals)
parks <- parks %>% mutate(Share = Visitors/YearTotal)

# get top 10 parks
parkTotals <- parks %>%
    filter(Year==2016) %>%
    arrange(-Visitors)
top10 <- parkTotals$ShortName[1:10]
```

